\documentclass[11pt,a4paper,roman]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')
\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                                % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page
\usepackage[utf8]{inputenc}
\usepackage{fontawesome}
\usepackage{fontspec}
\usepackage{tabularx}
\usepackage{ragged2e}
\usepackage[scale=0.9]{geometry}
\usepackage{multicol}
\usepackage{import}
\usepackage{color}
\usepackage[dvipsnames]{xcolor}

\definecolor{DarkBlue}{rgb}{0, 0, 0.7}
% personal data
\name{A}{Redditor}
% \title{Curriculum Vitae}                               % optional, remove / comment the line if not wanted
\address{420 Random Street, X1X 1X1, Vancouver, BC, Canada }{}{}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
  
\newcommand*{\customcventry}[7][.25em]{
  \begin{tabular}{@{}l} 
    {\bfseries #4}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\bfseries #5}
  \end{tabular} \\
  \begin{tabular}{@{}l} 
    {\itshape #3}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\itshape #2}
  \end{tabular}
  \ifx&#7&%
  \else{\\%
    \begin{minipage}{\maincolumnwidth}%
      \footnotesize #7%
    \end{minipage}}\fi%
  \par\addvspace{#1}}

\newcommand*{\customcvsubentry}[7][.25em]{
  \begin{tabular}{@{}l} 
    {\itshape #3}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\itshape #2}
  \end{tabular}
  \ifx&#7&%
  \else{\\%
    \begin{minipage}{\maincolumnwidth}%
      \footnotesize #7%
    \end{minipage}}\fi%
  \par\addvspace{#1}}

\newcommand*{\customcvproject}[4][.25em]{
%   \vfill\noindent
  \begin{tabular}{@{}l} 
    {\small\bfseries #2} % Apply small font size to the project title
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\footnotesize\itshape #3} % Apply small font size to the project date 
  \end{tabular}
  \ifx&#4&%
  \else{\\%
    \begin{minipage}{\maincolumnwidth}%
      \footnotesize #4 %Apply small font size to the project description
    \end{minipage}}\fi%
  \par\addvspace{#1}}


\setlength{\tabcolsep}{12pt}
\begin{document}

\makecvtitle
\vspace*{-23mm}

\begin{center}
\begin{tabular}{ c c c c }
  \faLanguage\enspace English/French &\faEnvelopeO\enspace me@redditor.com & \faGithub\enspace \href{https://github.com/Herbrax}{GitHub} & \faMobile\enspace 420-696-1337 \\  
\end{tabular}
\end{center}

\section{SKILLS}
  \textbf{Programming:} Python, Java, C, C#, Lua, HTML/CSS, Javascript, Julia\\*
  \textbf{Data:} SQL, Firebase, Pandas, Numpy\\*
  \textbf{Miscelleanous:} Git, Android Studio, Arduino/ESP32, Raspberry Pi, SketchUp, Photoshop, LaTeX\\*
  \textbf{Interests:} Astrophotography, Virtual Reality, Piano, Investing, Traveling, 3D Printing
  
 \section{EDUCATION}

{\customcventry{2020 - 2024}{B.Sc. in Computer Sciences}{University of Somewhere}{}{}
{\textcolor{DarkBlue}{Currently pursuing}, with an anticipated completion in April 2024.}
}
{\customcvsubentry{2022 - 2023}{Certificate in Applied Computer Sciences}{}{}{}
{Completed as part-time evening courses alongside my role at Evil AI, for ongoing academic development.}
}
\section{EXPERIENCE}
{\customcventry{2023 - Present}{Deputy Internal VP // Graduating Students Representative}{StudentAssociationName}{Vancouver, BC}{}
{\begin{itemize}
    \item Engaged in my student association as the representative for graduating students and as a member of the Representation Committee, contributing to the advocacy and support of student interests and needs.
\end{itemize}
}
{\customcventry{2022 - 2023}{Quality Team Lead}{Evil AI}{Vancouver, BC}{}
{\begin{itemize}
    \item As QA Team Lead, oversaw a diverse team, maintaining high-quality standards in big data processing, closely aligned with client objectives. Led initiatives to enhance workflows and data processing pipelines, improving efficiency and accuracy. Developed tools reducing error rates by 20\% and increasing productivity.
\end{itemize}
}
{\customcventry{2019 - 2021}{Supervisor}{WeSellRTX4090s}{Vancouver, BC}{}
{\begin{itemize}
    \item Driven by a fervent interest in hardware and cutting-edge technologies, leveraged product knowledge and interpersonal skills to deliver exemplary customer experience while aligning with management expectations.
\end{itemize}
}
\section{PROJECTS}
\customcvproject{Classification of Extreme Weather Events (Kaggle)}{}
{\begin{itemize}
  \item Engaged in a Kaggle competition aimed at the detection and classification of extreme weather events using climate data. 
  \item Developed models using logistic regression, SVM linear, and XGBoost, gaining proficiency in data handling and machine learning techniques.
\end{itemize}
}

{\customcvproject{ASCII Sign Language Classification (Kaggle)}{}
{\begin{itemize}
  \item Engaged in a Kaggle competition aimed at classifying sign language images and performing ASCII value manipulations.
  \item Implemented Random Forest and CNN models, furthering experience in machine learning and image processing, and utilized XGBoost for enhanced performance.
\end{itemize}
}

{\customcvproject{FishHunt (JavaFX Game)}{}
{\begin{itemize}
  \item Developed a JavaFX-based game where players control a shark to catch fish, with score-based increasing difficulty, special fish behaviors, and score tracking. Implemented using Model-View-Controller architecture and included features like dynamic fish movement, level progression, and a high-score system with data persistence.
\end{itemize}
}
{\customcvproject{Yu-Gi-Oh Inventory CSV Manager}{}
{\begin{itemize}
  \item Developed a script to manage a personal Yu-Gi-Oh card collection, processing raw inventory data from a CSV file and integrating TCGPlayer API to display detailed information on card prices and rarity.
\end{itemize}
}
}
\newpage

\nocite{*}
\bibliographystyle{plain}
\bibliography{publications}                        % 'publications' is the name of a BibTeX file


\end{document}

