\documentclass[11pt,a4paper,roman]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')
    \moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
    \moderncvcolor{blue}                                % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
    \nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page
    \usepackage[utf8]{inputenc}
    \usepackage{fontawesome}
    \usepackage{fontspec}
    \usepackage{tabularx}
    \usepackage{ragged2e}
    \usepackage[scale=0.9]{geometry}
    \usepackage{multicol}
    \usepackage{import}
    \usepackage{color}
    \definecolor{DarkBlue}{rgb}{0, 0, 0.7}
    \newcommand*{\customcventry}[7][.25em]{
    \begin{tabular}{@{}l} 
        {\bfseries #4}
    \end{tabular}
    \hfill% move it to the right
    \begin{tabular}{l@{}}
        {\bfseries #5}
    \end{tabular} \\
    \begin{tabular}{@{}l} 
        {\itshape #3}
    \end{tabular}
    \hfill% move it to the right
    \begin{tabular}{l@{}}
        {\itshape #2}
    \end{tabular}
    \ifx&#7&%
    \else{\\%
        \begin{minipage}{\maincolumnwidth}%
        \footnotesize #7%
        \end{minipage}}\fi%
    \par\addvspace{#1}}
    \newcommand*{\customcvproject}[4][.25em]{
    %   \vfill\noindent
    \begin{tabular}{@{}l} 
        {\small\bfseries #2} % Apply small font size to the project title
    \end{tabular}
    \hfill% move it to the right
    \begin{tabular}{l@{}}
        {\footnotesize\itshape #3} % Apply small font size to the project date
    \end{tabular}
    \ifx&#4&%
    \else{\\%
        \begin{minipage}{\maincolumnwidth}%
        \footnotesize #4 %Apply small font size to the project description
        \end{minipage}}\fi%
    \par\addvspace{#1}}
    \setlength{\tabcolsep}{12pt}
    % Personal Data/ %
    \name{Simo}{Hakim}
    \address{4390 Grand Boulevard, unit 302, H4B 2X8, Montreal, QC, Canada}
    % Personal Data\ %

    \begin{document}

    \makecvtitle
    \vspace*{-23mm}
    
    \begin{center}
    \begin{tabular}{ c c c c }
    % Contact line/ %
    \faLanguage\enspace English, French &\faEnvelopeO\enspace me@simohakim.com & \faGithub\enspace \href{https://github.com/Herbrax}{GitHub} & \faMobile\enspace +1 (438) 812-9242 \\
    % Contact Line\ %
    \end{tabular}
    \end{center}
    
    \section{ABOUT}
    % About Section/ %
    As I approach the completion of my Computer Science degree at the University of Montreal, I'm on the lookout for a Software Engineering internship where I can further build my stack and dive into real-world projects.
    % About Section\ %
    
    \section{SKILLS}
    % Resume Skills/ %
    \textbf{Programming:} Python, Java, C, C#, Lua, HTML/CSS, Javascript, Typescript, Julia\\*
    \textbf{Data:} SQL, Firebase, Tensorflow, PyTorch, Pandas, Numpy\\*
    \textbf{Miscellaneous:} Git, Android Studio, Arduino/ESP32, Raspberry Pi, SketchUp, Photoshop, LaTeX, Agile
    % Resume Skills\ %
    \section{EDUCATION}
% Education/ %
{\customcventry{2020 - 2024}{B.Sc. in Computer Sciences}{University of Montreal}{}{}
{Currently pursuing, with an anticipated completion in April 2024.}
}
{\customcventry{2022 - 2023}{Certificate in Applied Computer Sciences}{University of Montreal}{}{}
{Completed as part-time evening courses alongside my role at LXT AI, for ongoing academic development.}
}
{\customcventry{2019 - 2020}{Minor in Sciences}{University of Montreal}{}{}
{A concentrated focus in Computer Sciences and Physics.}
}
% Education\ %
\section{EXPERIENCE}
% Experience/ %
{\customcventry{2023 - Present}{Deputy Internal VP + Graduating Students Representative}{AEDIROUM (Student Association)}{Montreal, QC}{}
{\begin{itemize}
    \item Engaged in my student association as the representative for graduating students and as a member of the Representation Committee, contributing to the advocacy and support of student interests and needs.
\end{itemize}
}}
{\customcventry{2022 - 2023}{Quality Team Lead: GCP Subprocessor Speech-To-Text}{LXT AI}{Montreal, QC}{}
{\begin{itemize}
    \item Oversaw a team of 20, upholding high-quality standards in big data processing, closely aligned with client objectives
    \item Led initiatives to enhance workflows and data processing pipelines, resulting in improved efficiency and accuracy
    \item Developed and implemented tools and trainings that reduced error rates by 20% and increased overall team productivity.
\end{itemize}
}}
{\customcventry{2019 - 2021}{Supervisor}{Canada Computers}{Montreal, QC}{}
{\begin{itemize}
    \item Driven by a fervent interest in hardware and cutting-edge technologies, leveraged product knowledge and interpersonal skills to deliver exemplary customer experience while aligning with management expectations.
\end{itemize}
}}
% Experience\ %
\section{PROJECTS}
% Projects/ %
{\customcvproject{Classification of Extreme Weather Events (Kaggle)}{}
{\begin{itemize}
  \item Engaged in a Kaggle competition aimed at the detection and classification of extreme weather events using climate data
  \item Developed models using logistic regression, SVM linear, and XGBoost.
\end{itemize}
}}
{\customcvproject{ASCII Sign Language Classification (Kaggle)}{}
{\begin{itemize}
  \item Participated in a Kaggle competition to classify sign language images
  \item Implemented Random Forest and CNN models, utilizing XGBoost for enhanced performance.
\end{itemize}
}}
{\customcvproject{FishHunt (JavaFX Game)}{}
{\begin{itemize}
  \item Developed a JavaFX-based game simulating a shark catching fish
  \item Implemented dynamic fish movement, level progression, and a high-score system.
\end{itemize}
}}
{\customcvproject{Yu-Gi-Oh Inventory CSV Manager}{}
{\begin{itemize}
  \item Made a script for managing a Yu-Gi-Oh card collection, integrating TCGPlayer API for detailed card information.
\end{itemize}
}}
% Projects\ %
\end{document}